---
title: "An Example of using Word export in R Markdown"
author: "An Aspiring R Markdown User"
date: "08/03/2022"
output:
  word_document:
    reference_docx: ../assets/apa.docx
---

# More Complex Data Analysis

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse) # defaults
library(knitr) # for kable function
library(qwraps2) # for in-text means example
library(skimr) # for summary statistics
library(apa) # for t_apa function


# This is just setting up the data
chopstick_data = read.csv("./data/chopstickdata.csv") %>% 
  relocate(Subject, ChopstickLength, FoodPinchingEff) %>% 
  mutate(ChopstickLength = as.factor(ChopstickLength), 
         Subject = as.factor(Subject)) %>% 
  arrange(ChopstickLength, Subject)

# And getting our demographics information
demogr = read.csv("./data/demographics.csv")

# Ignore until later in lesson
# demogr = read.csv("../data/demographics.csv") %>% filter(subjectid < 24)

```

```{r}
# This just lays out the t-tests etc for reporting example only.
chopstick_data_wide = chopstick_data %>% 
  pivot_wider(id_cols = Subject, values_from = FoodPinchingEff, names_from = ChopstickLength)

ttest180 <- t.test(chopstick_data_wide$`240`, chopstick_data_wide$`180`, paired=T)
ttest0 <- t.test(chopstick_data_wide$`240`, chopstick_data_wide$`210`, paired=T)
ttest1 <- t.test(chopstick_data_wide$`240`, chopstick_data_wide$`270`, paired=T)
ttest2 <- t.test(chopstick_data_wide$`240`, chopstick_data_wide$`300`, paired=T)
ttest3 <- t.test(chopstick_data_wide$`240`, chopstick_data_wide$`330`, paired=T)
```


The 240mm was associated with a signficantly higher Food Pinching Efficiency than 
the 180mm, `r t_apa(ttest180, es = "cohens_d", format = "markdown", print = FALSE)`; 
the 270mm `r t_apa(ttest1, es = "cohens_d", format = "markdown", print = FALSE)`; 
the 300mm `r t_apa(ttest2, es = "cohens_d", format = "markdown", print = FALSE)`; 
and the 330mm `r t_apa(ttest3, es = "cohens_d", format = "markdown", print = FALSE)`. 
However, there was no difference in Food Pinching Efficiency between 
the 210mm and 240mm, `r t_apa(ttest0, es = "cohens_d", format = "markdown", print = FALSE)`.

# Plotting

```{r}
ggplot(data = chopstick_data, aes(ChopstickLength,FoodPinchingEff)) +
  geom_boxplot(aes(color=ChopstickLength)) + 
  theme(legend.title=element_blank()) + 
  geom_jitter(width = 0.2, alpha=0.2)

```
